### 2024-05-01 article.tex
minor fix

\section{Dataset Analysis}
As two mediums vision and audio are being used for classification of animals, two different datasets comprising of labeled images and labeled audio is required. ImageNet was our initial choice for image data but due to misrepresentaions of species, the idea was dropped and iNaturalist was choses as our final source for image data.\cite{r10} 
The image dataset has a total of 44 classes. Of the 44 classes, there are 31 mammals, 9 birds, and 4 reptiles. Moreover, we couldn’t find research-grade audio data for groups of animals other than birds. Thus, the audio model comprises 23 classes of birds all found in Nepal.
\subsection{Image Data from iNaturalist}
iNaturalist is an online social network of people sharing biodiversity information which has been extensively used for developing ML-powered species identifications. It has a large size of data which includes images, audio, and video of large number of species found around the world. The data is collected by users who submit it to the site under the public domain, Creative Commons, or with all rights reserved. iNaturalist encourages its users to opt for more open licenses like Creative Commons for the research community.We collected a total of 38,442 images spanning across 44 species all found in Nepal. As the data contained some anomalous images, we had to manually remove them. After the cleaning step, the data was preprocessed as per the Efficient Net Model for better training. Of the 38,442 images collected, 50 images from each class were used as test datasets.
API provided by iNaturalist was used for downloading the data. The following bar chart shows the frequency of each class of image
	{

>>>>

\section{Dataset Analysis}
As two mediums vision and audio are being used for classification of animals, two different datasets comprising of labeled images and labeled audio is required. ImageNet was our initial choice for image data but due to misrepresentaions of species, the idea was dropped and chose iNaturalist as our final source for image data for its reliability and proper representation.\cite{r10}
\par
The image dataset has a total of 44 classes. Of the 44 classes, there are 31 mammals, 9 birds, and 4 reptiles. Moreover, we couldn’t find research-grade audio data for groups of animals other than birds. Thus, the audio model comprises 23 classes of birds all found in Nepal.
\subsection{Image Data from iNaturalist}
iNaturalist is an online social network of people sharing biodiversity information which has been extensively used for developing ML-powered species identifications. It has a large size of data which includes images, audio, and video of large number of species found around the world. The data is collected by users who submit it to the site under the public domain, Creative Commons, or with all rights reserved. iNaturalist encourages its users to opt for more open licenses like Creative Commons for the research community.
\par
We collected a total of 38,442 images spanning across 44 species all found in Nepal. As the data contained some anomalous images, we had to manually remove them. After the cleaning step, the data was preprocessed as per the Efficient Net Model for better training. Of the 38,442 images collected, 50 images from each class were used as test datasets.
API provided by iNaturalist was used for downloading the data. The following bar chart shows the frequency of each class of image
	{
